---
title: "tirt"
author: "Interpretational Threshold based on IRT method \n"
output: rmarkdown::github_document
always_allow_html: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This $R$ package contains the `tirt` function to estimate interpretational threshold values (with bootstrapped 95% CIs) of a multi-item questionnaire using the item response theory (IRT) method developed by [Terluin et al[^1]](https://pubmed.ncbi.nlm.nih.gov/36780033/). The package is developed to accompany the paper, "Using item response theory to estimate interpretation threshold values for the Frailty Index (FI) in community dwelling middle-aged and older adults."  Two example datasets are included in the package to help users better understand its functionality. 


[^1]: Terluin et al Estimating meaningful thresholds for multi-item questionnaires using item response theory Qual Life Res. 2023 Jun;32(6):1819-1830. doi: 10.1007/s11136-023-03355-8. Epub 2023 Feb 13.



## Installation
Install the development version from [GitHub](https://github.com/yhpua/tirt) with:

``` r
# install.packages("devtools")
devtools::install_github("yhpua/tirt")
```

## Example 1
Using `tirt` to estimate FI interpretational threshold. A built-in toy dataset `fi_dat` is used in the example code below. The dataset comprises all (binary and polytomous) items of the Frailty Index, and the last column represents a binary anchor item.   

Setting the `B = 100` argument specifies 100[^2] bootstrap resamples when computing 95%CIs for the IRT-based thresholds.  

[^2]: Should have specified more (e.g., $1000$) samples

```{r example1, cache = TRUE}
library(mirt)
library(tirt)
data(fi_dat)
summary(fi_dat)
tirt(fi_dat, B = 100)  
```


## Example 2
The built-in `qol_dat` dataset uses the simulated dataset provided in the supplementary materials of the paper by [Terluin et al](https://pubmed.ncbi.nlm.nih.gov/36780033/).    

Setting the `rform` argument to `sum` returns the expected (mean) questionnaire score. In Example 1, `rform` is set to `prop` (default) which expresses the expected score as a proportion of the number of items evaluated.    

```{r example2, cache=TRUE}
data(qol_dat)
tirt(qol_dat, B = 100, rform = "sum")
```


 
