---
title: "tirt"
author: "Interpretational threshold values based on the IRT method\n"
output: rmarkdown::github_document
always_allow_html: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This $R$ package contains the `tirt` function to estimate interpretational threshold values (with bootstrapped 95% CIs) of a multi-item questionnaire based on the item response theory (IRT) method developed by [Terluin et al[^1] ](https://pubmed.ncbi.nlm.nih.gov/36780033/). The package is developed to accompany the paper, "Using item response theory to estimate interpretation threshold values for the Frailty Index (FI) in community dwelling older adults."  Two example datasets are included in the `tirt` package to help users better understand its functionality. 


[^1]: Terluin et al Estimating meaningful thresholds for multi-item questionnaires using item response theory Qual Life Res. 2023 Jun;32(6):1819-1830. doi: 10.1007/s11136-023-03355-8.



## Installation
Please install the `tirt` package from [GitHub](https://github.com/yhpua/tirt) with:

``` r
install.packages("devtools")
devtools::install_github("yhpua/tirt")
```

## Example 1
We will use `tirt` to estimate the interpretational threshold value of the Frailty Index (FI). The built-in synthetic dataset, `fi_dat`, includes all (binary and polytomous) items of the FI and a (binary) clinical anchor item that is placed in the last column.     

Note that setting the `B = 100` argument specifies 100[^2] bootstrap resamples to be used when computing the 95%CIs for the IRT-based thresholds.    

[^2]: Should have specified more (e.g., 1000) samples

```{r example1, cache = TRUE}
library(mirt)
library(tirt)
data(fi_dat)
summary(fi_dat)
tirt(fi_dat, B = 100)  
```


## Example 2
We will use `tirt` to estimate the IRT-based threshold value of a multi-item questionnaire. The built-in `qol_dat` dataset is the simulated dataset described in Appendix Section 4 of the paper by [Terluin et al](https://pubmed.ncbi.nlm.nih.gov/36780033/).    

Note that setting the `rform` argument to `sum` returns the expected (mean) questionnaire score. In Example 1, we set `rform` to `prop` (default) which expresses the expected score as a proportion of the number of items evaluated.    

```{r example2, cache=TRUE}
data(qol_dat)
tirt(qol_dat, B = 100, rform = "sum")
```


 
